Practical Effects of Integrating Temperature with Strang Split Reactions

### 2021-03-17 strang/paper.tex
update line styles

\begin{figure}[t]
\centering
\plotone{test}
\caption{\label{thefigure} Convergence of fluid quantities as a function of resolution
for 3 different Strang equation systems: just evolving $X_k$, evolving $(X_k, T)$, but fixing $c_v$ at the start of integration (``frozen''), and evolving $(X_k, e)$.}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\plotone{test}
\caption{\label{thefigure} Convergence of fluid quantities as a function of resolution
for 3 different Strang equation systems: just evolving $X_k$, evolving $(X_k, T)$ with $c_v$ held fixed, and evolving $(X_k, e)$.}
\end{figure}
